Bayesian calibration of a hybrid nuclear collision model\\ using $\boldsymbol p$-Pb and Pb-Pb data from the LHC

### 2019-03-20 paper/paper.tex
dissertation

Typically, the macroscopic structure of heavy nuclei, characterized e.g.\ by an atomic mass number and set of Woods-Saxon coefficients \cite{MOLLER1995185, DEVRIES1987495}, is regarded as a known input to hydrodynamic models which contributes negligible uncertainty to simulation predictions, outweighed by large uncertainties in modeling initial energy deposition and off-equilibrium dynamics \cite{Niemi:2014lha, Song:2011hk, Retinskaya:2013gca, Liu:2015nwa, Kurkela:2016vts}.
The geometry of light ions, meanwhile, is naturally more sensitive to the detailed size and shape of individual protons and neutrons inside the nucleus, which may fluctuate event-by-event and differ signficantly from the round blobs typically used to approximate nucleons in heavy-ion collisions \cite{Schenke:2014zha, Welsh:2016siu, Moreland:2017kdx, Schenke:2014gaa, Schlichting:2014ipa}.
These nucleon substructure properties are difficult to measure and calculate from first principles and hence contribute significant uncertainty to model predictions of small systems.

>>>>

Typically, the macroscopic structure of heavy nuclei, characterized e.g.\ by an atomic mass number and set of Woods-Saxon coefficients \cite{MOLLER1995185, DEVRIES1987495}, is regarded as a known input to hydrodynamic models which contributes negligible uncertainty to simulation predictions, outweighed by large uncertainties in modeling initial energy deposition and off-equilibrium dynamics \cite{Niemi:2014lha, Song:2011hk, Retinskaya:2013gca, Liu:2015nwa, Kurkela:2016vts}.
The geometry of light ions, meanwhile, is naturally more sensitive to the detailed size and shape of individual protons and neutrons inside the nucleus, which may fluctuate event-by-event and differ significantly from the round blobs typically used to approximate nucleons in heavy-ion collisions \cite{Schenke:2014zha, Welsh:2016siu, Moreland:2017kdx, Schenke:2014gaa, Schlichting:2014ipa}.
These nucleon substructure properties are difficult to measure and calculate from first principles and hence contribute significant uncertainty to model predictions of small systems.
